---
title: "Project 1"
author: 'Konark Mangudkar, '
output:
  html_document:
    df_print: paged
---

```{r, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	echo = FALSE, # hide all R codes!!
	fig.width=5, fig.height=4,#set figure size
	fig.align='center',#center plot
	options(knitr.kable.NA = ''), #do not print NA in knitr table
	tidy = FALSE #add line breaks in R codes
)
```

#Introduction
......
Half page introduction includes background about the problem, description of the data, main objectives of your study, main tool(s) you use, an outline of the rest of the report.
......

#Part I: Fitting regression models

##Projects 1.43 
(a) Regress the number of active physicians in turn on each of the three predictor variables. State the estimated regression functions.


```{r, results="hide"}
#use results="hide" to hide the unimportant output.
pop <- read.csv("CDI.txt", sep="")
n = length(pop$id)
Y = pop$numphys

# 1.43.a
X1 = pop$totalpop ; X2 = pop$numbeds ; X3 = pop$totalpersonalincome
totalpopregress = lm(Y ~ X1) ; numbedsregress = lm(Y ~ X2) ; personincomeregress = lm(Y ~ X3)
totalpopregress$coefficients[1]
totalpopregress$coefficients[2]
# Y1 = -110.6348 + 0.002795425*X






# 1.43.b
plot(X1, Y)
abline(totalpopregress)


# 1.43.c
totalpopanova = anova(totalpopregress)
numbedsanova = anova(numbedsregress)
personincomeanova = anova(personincomeregress)
totalpopanova$`Mean Sq`[2]
numbedsanova$`Mean Sq`[2]
personincomeanova$`Mean Sq`[2]
```

Let $Y$ be breakage, $X_1$ be the number of transfers. The estimated regression function is $\hat{Y}= `r b0hat`+ `r b1hat` X_1$.

*#Define $X$ and $Y$ clearly, and only answer the questions, do not need to show the formulas for the calculations.*

......


(b) Plot the three estimated regression functions and data on separate graphs. Does a linear regression relation appear to provide a good fit for each of the three predictor variables?

```{r}
#Fitted line
plot(X,Y,ylim=c(5,30),xlab = "Number of transfer",ylab = "Number of broken ampules")
abline(fit, col="red")
```

....Label the axes clearly, Comments on the plot...

#Part II: Measuring linear associations

#Part III: Inference about regression parameters

#Part IV: Regression diagnostics

#Part V: Discussion

#Appendix
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
